Uncertainty-aware graph-based multimodal remote sensing classification

### 2021-07-13 latex/CEUR/paper.tex
Update author info

\author[1]{A Nother}[orcid=0000-0000-0000-0000, email=another@vu.nl,]

\author[1]{A Nother}[orcid=0000-0000-0000-0000,email=another@acm.org,]

>>>>

\author[1,2]{Andrea~Marinoni}[orcid=0000-0001-6789-0915, email=andrea.marinoni@uit.no,]

\author[1]{Sivasakthy~Selvakumaran}[orcid=0000-0002-8591-0702,email=ss683@cam.ac.uk,]
